|

### 2021-05-30 article/article.Rmd
fix paper list

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1.1cm}}
\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
\toprule
\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
\tabularnewline
\midrule
\endhead 
```{r papers, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authoryear, journalCode, locationISO, depvar2, method, instdesign, elecsys3, year) %>%
  unique() %>%
  arrange(year)
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authoryear[i]), ' & ', aux$journalCode[i], ' & ',
      aux$locationISO[i], ' & ', aux$depvar2[i], ' & ', 
      aux$method[i], ' & ', aux$instdesign[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Journal:} Unpub$=$Unpublished, JPE$=$Journal of Political
Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal.}
\footnotetext{\textbf{Country:} Country codes follow the ISO 3166-1 alpha-3
international standard.} 
\footnotetext{\textbf{Dependent Variable:} ExpPC$=$Per capita expenditure,
logExpPC$=$Natural logarithm of per capita expenditure, PCTGDP$=$Expenditure as
a percentage of GDP.}
\footnotetext{\textbf{Method:} OLS$=$Ordinary least squares, IV$=$Instrumental
variables, Panel$=$Panel data/fixed effects, RDD$=$Regression discontinuity
design.}
\footnotetext{\textbf{Electoral System:} M$=$Majoritarian, NM$=$Non-majoritarian (mixed or proportional
representation).} 
\end{minipage} 
\end{longtable}
\normalsize

>>>>

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1.1cm}}
\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
\toprule
\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
\tabularnewline
\midrule
\endhead 
```{r papers, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authoryear, journalCode, locationISO, depvar2, method, instdesign, elecsys3, year) %>%
  unique() %>%
  arrange(year, depvar2)
aux2 <- aux %>%
  mutate(depvar2 = 'aux') %>%
  unique()
for(i in 1:dim(aux)[1]) {
  if(aux2$depvar2[aux2$authoryear == aux$authoryear[i]] == 'aux') {
    aux2$depvar2[aux2$authoryear == aux$authoryear[i]] = aux$depvar2[i]
  } else {
    aux2$depvar2[aux2$authoryear == aux$authoryear[i]] = paste(
      aux2$depvar2[aux2$authoryear == aux$authoryear[i]],
      aux$depvar2[i], sep = ', ')
  }
}
aux <- aux2
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authoryear[i]), ' & ', aux$journalCode[i], ' & ',
      aux$locationISO[i], ' & ', aux$depvar2[i], ' & ', 
      aux$method[i], ' & ', aux$instdesign[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Journal:} Unpub$=$Unpublished, JPE$=$Journal of Political
Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal.}
\footnotetext{\textbf{Country:} Country codes follow the ISO 3166-1 alpha-3
international standard.} 
\footnotetext{\textbf{Dependent Variable:} ExpPC$=$Per capita expenditure,
logExpPC$=$Natural logarithm of per capita expenditure, PCTGDP$=$Expenditure as
a percentage of GDP.}
\footnotetext{\textbf{Method:} OLS$=$Ordinary least squares, IV$=$Instrumental
variables, Panel$=$Panel data/fixed effects, RDD$=$Regression discontinuity
design.}
\footnotetext{\textbf{Electoral System:} M$=$Majoritarian, NM$=$Non-majoritarian (mixed or proportional
representation).} 
\end{minipage} 
\end{longtable}
\normalsize
